### 2022-06-20 paper.tex
fmt

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

>>>>

Lukas P.~M.~Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}
